Random forest mill rates

### 2020-04-11 src/modeling - 550/rf_mill.Rmd
deleted comment

dat_as <- dat %>% 
  left_join(factors_tbl) %>% 
  select(-c(municipality)) %>% 
  rename(municipality = col_municipality) %>% 
  group_by(PIC) %>% 
  arrange(year) %>% 
  mutate(next.assess = lead(total.assessment, order_by = year),
         past.mill = lag(mill.rate, order_by = year))

# 
# notwant <- c("CA-BC-003-6500000", "CA-BC-223-00100030000", "CA-BC-227-0000020000", "CA-BC-234-01001006", "CA-BC-301-0000001", "CA-BC-315-00001000","CA-BC-316-010012122009", "CA-BC-336-00001000", "CA-BC-338-1000004884000", "CA-BC-556-00001000", "CA-BC-727-03025100", "CA-BC-757-05141000", "CA-BC-759-000147000", "CA-BC-760-001203000", "CA-BC-765-00002001", "CA-BC-771-00003000")

>>>>

dat_as <- dat %>% 
  left_join(factors_tbl) %>% 
  select(-c(municipality)) %>% 
  rename(municipality = col_municipality) %>% 
  group_by(PIC) %>% 
  arrange(year) %>% 
  mutate(next.assess = lead(total.assessment, order_by = year),
         past.mill = lag(mill.rate, order_by = year)) %>% 
  na.omit()
